CAT-DWAM, A Question Answering System

### 2011-05-07 paper/paper.tex
paper

>>>>

\subsection{Walk through of one question}
- Initial setup of the Q/A system
    - We collect all the documents that may contain the answer for all qids (20 documents per qid)
    - We then run the chunker on the document text creating answer candidate phrases
    - We save the chunker results to a set of files
- We are given a question id
- We retrieve the question text from the provided input file
- We read the chunker results 
    - We filter out all candidate answers that are not noun phrases
    - We also filter out candidate answers not within 50 bytes of the aligned question in the document
- We feed the filtered answers through our answer evaluators specifically
    - punctuation_location,
    - novelty_factor
    - a combination of both
- The scores of the evaluators are fed into the supervised classification algorithm:
    - Spectral Regression Discriminant Analysis 
    - this gives us a confidence measure
- Sort by confidence measure 
- In descending order by confidence measure, pack them into 50-byte answers which are our final outputs
- The answers are then passed into our scorer
